Tables with \textbf{xtable} and \textbf{knitr}

### 2016-10-02 src/ArticleReadyTableGenerate.Rnw
turn off warnings

<<Pooled_Stat_Tests, cache=TRUE>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
  hypothesis_ordinality <- c("two.sided","less","greater")

@@

      #read the pooled files 
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        pooled_stats <- scan(file=cond_fileh)
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- as.vector(pooled_stats[,1])
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
      }
      #print(str(pool_stats_all[side,region]))
      print(str(pooled_stats_list))
      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
      #pool_stats_all[side,region] <- pooled_stats_list

@@

        p_values$welch.t.test[i,][test.type] <-welch.t.test.result$p.value
       pooled_test_results[[i]][[test.type]]<-vector(mode="list",length = 3 )
       print(str(pooled_test_results[[i]][[test.type]]))
       pooled_test_results[[i]][[test.type]]<-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
       print(str(pooled_test_results[[i]][[test.type]]))
      }

>>>>

<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
  hypothesis_ordinality <- c("two.sided","less","greater")

@@

      #read the pooled files 
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        pooled_stats <- scan(file=cond_fileh)
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- as.vector(pooled_stats[,1])
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
      }
      #print(str(pool_stats_all[side,region]))
      #print(str(pooled_stats_list))
      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
      #pool_stats_all[side,region] <- pooled_stats_list

@@

        p_values$welch.t.test[i,][test.type] <-welch.t.test.result$p.value
       pooled_test_results[[i]][[test.type]]<-vector(mode="list",length = 3 )
       #print(str(pooled_test_results[[i]][[test.type]]))
       pooled_test_results[[i]][[test.type]]<-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
       #print(str(pooled_test_results[[i]][[test.type]]))
      }
